\chapter*{Acknowledgements}

The past four years have been simultaneously incredibly rewarding and challenging.
Without the love and support I have received from the many friends, family members and colleagues I have spent this time with, I know that I would have achieved little, and enjoyed it far less.
First, I would like to thank my supervisor, Jerry, who has provided me with much advice, support and guidance.
I think that my three-month side project of making a CBET model might almost be finished.

The many members, past and present, of CIFS and the wider Imperial plasma group have made each and every day working here a pleasure, and I would like to thank them all.
Particularly (in alphabetical order) Adam D. for being an excellent Griffin replacement, Adam F. for being unceasingly joyful, Aidan B. for helping me to overcome (some) of my squeamishness, Aidan C. for knowing everything about everything, Ben for giving me a good fructose and breakfast sausage contest, Brian for some amazing pre-conference trips, Dom for the best (and toughest) bike ride of my life, Nic for teaching me how to surf, Niki for many cups of tea, advice and chat, and Sam for our fruitful collaborations.

I am delighted to have such good friends outside of work as well.
Huge thanks to Tom and Ronan.
It scares me to think that soon we will have lived apart for as long/ longer than we lived together!
I am not sure that I would have made it through my undergrad, let alone a PhD, if I didn't have you both as incredible friends.
Thanks also to my many other friends and housemates from my time in London, particularly Tommy M., Greg, Silvia, Liv and Chris.
I look forward to many more weekend gatherings, general silliness and trips away with Ben, Push and Robbo.
Regularly seeing you guys makes me laugh and reconnects me to home.
Special thanks to Griff.
It still feels weird not seeing you every day, but your friendship and support has been constant through these four years, and I am incredibly grateful for it.

So much thanks to my family.
I feel so privileged that there are too many of you to name each individually, but I love spending time with each and every Moloney, Cowie, Phillips and Thomas.
In particular, I must mention Rory and Granny, who I miss hugely.
Feeling like a big, fun cousin to Rory helped shape me as a teenager and I know that Granny would have truly loved to see me finish my PhD. 
Mum, dad and Liv, what can I say.
I don't know what you could have done to support me more over the past four years, and the twenty-three years before that.
You are the best family I could have asked for.

Finally, to Ewa.
You've been by my side from first applications all the way through to now, and every day you've made me smile and feel loved.
I wouldn't be where I am without you.
All my love and gratitude goes to you.
