\chapter*{Role of the Author}

The research presented in this manuscript has been conducted using the multidimensional \textsc{Chimera} \ac{Rad-MHD} code.
\textsc{Chimera}, a variant of which is also referred to as \textsc{Gorgon}, is developed and maintained by the \ac{CIFS} at Imperial College London~\cite{chittenden_xray_2004}.
Many authors have contributed to the development of this code over two decades.
All simulations discussed in this manuscript were carried out by the author of this thesis.
Analyses of the results presented in this manuscript are the work of the author of this thesis.
The \textsc{Solas} laser ray-tracing and \ac{CBET} module was developed by the author and is presented in Chap.~\ref{chap:SOLAS}.
All development, implementation and debugging of this solver was the work of the author of this thesis.
Most of the test problems used to validate \textsc{Solas} are the work of other authors, who are referenced.
The field reconstruction and \ac{CBET} test problems, published by Russ Follett \textit{et. al.} in Ref.~\cite{follett_validation_2022}, were particularly helpful to validate the solver.
Analysis of the results from these test problems was carried out by the author of this thesis.
The previous laser ray-trace module was developed by Christopher Walsh, and some functions from \textsc{Solas} are based on this implementation.
The author also contributed to the development of other aspects of the code, including the thermal conduction module, which is not presented in this thesis.
Initial conditions for the magnetised simulations conducted in Chap.~\ref{chap:Mag} were provided by Cody Wu Chang and Johan Frenje at the \ac{MIT}.
These simulations were based on experiments conducted at the \textsc{OMEGA} laser facility at the \ac{LLE}.
Consultation and advice about implementation and usage of the \textsc{Chimera} code came from all members of \ac{CIFS}.
Permissions for any external copyrighted material used can be found in Appendix~\ref{app:permissions}.